Kyoto VR MQP Paper First Draft

### 2019-09-20 paper.tex
worked on more sections

@@

\subsubsection{Adobe XD Design}
\label{sec:aruko}
On September 10th, Atticus Sims presented us with a storyboard for the app
experience. We would not be able to resume work until September 17th due to
prior travel plans. Whether Atticus knew this or not, the design he put forth
had ramifications that rippled throughout the entire software stack we had
constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows this design.

@@

One of the notable changes is the chapter select screen, which is the third
screen in Figure~{fig:adobeXdDesign}. Before, we worked under the assumption
that each geolocation-triggered region would not have to be ordered in any way.
This assumption made its way into Editour, which did not currently have a way
to reorder regions once they were placed. Because of this chapter selection
screen, we needed some way to rearrange the order of regions within Editour.

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI. This was disappointing to us, since we spent
a great deal of effort projecting images into the 3D world using the AR camera;
we felt like we figured out how to use this technology in a way that was both
usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
the 3D world, such as by framing the images in a traditional Japanese pagoda,
which would fit in with the environment. On the same screen, there is a
scrollable window of text for a transcript of the audio. Because of this, the
Editour UI and tour metadata JSON file needed to be updated to accomodate a
transcript per region. On top of this, the C\# code that interprets the tour
file needed to be updated to expect an audio transcript field.
Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
to add these new features. The arrows next to the region name can be used to
move the "Region Card" up and down in the side bar. In the "Media" tab, there
is also a text area to include a transcript of the uploaded audio file.

@@

In Editour, the frontend alone was already around three thousand lines of
vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
the growing code complexity more manageable. Excluding Node modules, the only
external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps \autocite{leafletjs}. We did not use any libraries
for developing frontends like Facebook's React or Google's Angular. Instead,
all of the complex UI interactions were handled by modifying the DOM directly
with JavaScript's built-in functionality. Furthermore, we did not use any
advanced frontend build tools such as Rollup, webpack or Parcel. This was
likely an appropriate decision for a JavaScript project of this scope, but if
we were to continue to develop Editour, UI libraries and frontend build tools
would be something to consider.

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkakuji for us to use as
image targets. In this design, the AR camera superimposes an "info" button on
top of the sign. Tapping on this button brings up a separate UI element
containing the translation, which can be seen in Figure~\ref{fig:signTranslation}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{sign-translation.png}
	\caption[Additions to the editour to accommodate the new design]
    {Additions to the editour to accommodate the new design}
	\label{fig:signTranslation}
\end{figure}

ordering*
transcripts*
no more ground plane detection*
many, many image targets
thumbnails for the chapter

@@

>>>>

The company motive.io used to work on a product that would allow users to
create an engaging AR experience in the style of Pokemon Go. Their service
would have purportedly handled technical details such as hosting, storage, and
user accounts. The promotional video shows the creation of a location-based AR
game where the user pretends to hack into ATMs using the real-world locations
of ATMs in a city\autocite{odom2017}.

Unfortunately, it appears that the company has completely pivoted off of this
idea, and has since moved to AR training software\autocite{motiveio}.

We reached out to motive.io via email for any advice they might be willing to
give us, but we received no response.

@@

\subsubsection{Adobe XD Design}
\label{sec:adobeXdDesign}
On September 10th, Atticus Sims presented us with a storyboard for the app
experience. We would not be able to resume work until September 17th due to
prior travel plans. Whether Atticus knew this or not, the design he put forth
had ramifications that rippled throughout the entire software stack we had
constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows this design.

@@

One of the notable changes is the chapter select screen, which is the third
screen in Figure~\ref{fig:adobeXdDesign}. Before, we worked under the assumption
that each geolocation-triggered region would not have to be ordered in any way.
This assumption made its way into Editour, which did not currently have a way
to reorder regions once they were placed. Because of this chapter selection
screen, we needed some way to rearrange the order of regions within Editour.

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI. This was disappointing to us, since we spent
a great deal of effort projecting images into the 3D world using the AR camera;
we felt like we figured out how to use this technology in a way that was both
usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
the 3D world, such as by framing the images in a traditional Japanese pagoda,
which would fit in with the environment. On the same screen, there is a
scrollable window of text for a transcript of the audio. Because of this, the
Editour UI and tour metadata JSON file needed to be updated to accomodate a
transcript per region. On top of this, the C\# code that interprets the tour
file needed to be updated to expect an audio transcript field.
Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
to add these new features. The arrows next to the region name can be used to
move the ``Region Card'' up and down in the side bar. In the ``Media'' tab, there
is also a text area to include a transcript of the uploaded audio file.

@@

In Editour, the frontend alone was already around three thousand lines of
vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
the growing code complexity more manageable. Excluding Node.js modules, the only
external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps \autocite{leafletjs}. We did not use any libraries
for developing frontends like Facebook's React or Google's Angular. Instead,
all of the complex UI interactions were handled by modifying the DOM directly
with JavaScript's built-in functionality. Furthermore, we did not use any
advanced frontend build tools such as Rollup, webpack or Parcel. This was
likely an appropriate decision for a JavaScript project of this scope, but if
we were to continue to develop Editour, UI libraries and frontend build tools
would be something to consider. With these changing requirements, the Editour
was becoming onerous to maintain at this stage of the project.

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkakuji for us to use as
image targets. Hikaru Inoue helped us by translating all of the text in these
photos from Japanese to English. In this design, the AR camera superimposes an
``info'' button on top of the sign. Tapping on this button brings up a separate
UI element containing the translation, which can be seen in
Figure~\ref{fig:signTranslation}.

\begin{figure}[h] \centering
\includegraphics[width=0.5\textwidth]{sign-translation.png} \caption{Translated
sign using AR camera} \label{fig:signTranslation}
\end{figure}

As previously mentioned, Atticus initially wanted us to explore the efficacy of
using Vuforia's 2D image target capabilities for scanning objects outside of
the expected use case, such as 3D landscapes or the side of a building. We had
serious doubts about how well this would work, and our suspicions were
confirmed after some field testing. This was the reasoning behind focusing on
ground-plane detection instead of image targets; ground-plane detection can be
used anywhere, and is much more reliable than treating 3D objects as 2D image
targets.

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store, called ``Experience Importer - Adobe Xd files importer'', which claims
``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
objects. They're already there! Just drag .xd file to project and... voila!''
We suspect this sounds too good to be true because it is. As of September 20th,
2019, there are 6 user reviews. All of the five-star reviews were have the
caveat ``Reviewer was gifted package by publisher'' which which we interpreted
as a warning sign. Because of this, we decided to rebuild the UI largely from
the ground up, using the Adobe XD file to guide us.

@@

\section{Pivots}
\label{sec:pivots}

Throughout the duration of the project, the goalposts shifted multiple times.
This section details some of the initial plans that fell through.

\section{3D Spatialized Audio Tour}
\label{sec:3dSpatializedAudioTour}
